Effects of the body force on the pedestrian and evacuation dynamics

### 2020-02-07 paper.tex
modificaciones leves de formato

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the pedestrians desired velocity. Each symbol indicates the $k_n$ value corresponding to the body force (see the labels). The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians). The average was taken every five seconds once the crowd reached the stationary state (say, $t=20\,$s) until the end of the simulation ($t=1000\,$s). Color online only.}
\label{degree_overlap_vd}
\end{figure}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$ as a function of the stiffness $k_n$ for three different global densities (see label in the plot). The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. Color online only.      }
\end{figure}

@@

\begin{equation}
S = \frac{\langle v_x(center)\rangle - \langle v_x(boundary)\rangle }{\left | y(center) - y(boundary) \right |} 
\end{equation}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label). (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label). The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$. The global density was 7 p$\,$m$^{-2}$. Color online only. }
\label{profile_strain}
\end{figure}

@@

In this section, we inspect different values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$ and compare the results with the empirical measurements of Ref.~\cite{helbing_2007}. We varied the body force coefficient ($k_c$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\

@@

\begin{equation}
 \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
 \mathcal{K}=\displaystyle\frac{k_t\,B\,\tau}{m}\ \ \ \ , \ \ \ \
 \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m\,v_d}
\end{equation}

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the pedestrians desired velocity. Each symbol indicates the $k_n$ value corresponding to the body force (see the labels). The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians). The average was taken over time and the pedestrians in the bottleneck. The sampling was done every five seconds once the crowd reached the stationary state (say, $t=20\,$s) until the end of the simulation ($t=1000\,$s). Color online only.}
\label{degree_overlap_vd}
\end{figure}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$
 as a function of the stiffness $k_n$ for three different global densities (see label in the plot). 
 The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
 The average was taken along the corridor and along the simulated time. Color online only.      }
\end{figure}

@@

\begin{equation}
S = \frac{\langle v_x(\mathrm{center})\rangle - \langle v_x(\mathrm{boundary})\rangle }{\left | y(\mathrm{center}) - y(\mathrm{boundary}) \right |} 
\end{equation}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k_n$ (see the label). (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label). The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$. The global density was 7 p$\,$m$^{-2}$. Color online only. }
\label{profile_strain}
\end{figure}

@@

In this section, we inspect different values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$ and compare the results with the empirical measurements of Ref.~\cite{helbing_2007}. We varied the body force coefficient ($k_n$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\

@@

\begin{equation}
 \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
 \mathcal{K}=\displaystyle\frac{k_t\,B\,\tau}{m}\ \ \ \ , \ \ \ \
 \mathcal{K}_c=\displaystyle\frac{k_n\,B\,\tau}{m\,v_d}
\end{equation}
